
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\newpage
\vspace{0.7cm}
{\bf Publications}\\
\noindent\rule{\textwidth}{0.5pt}
%\vspace{0.2cm}
\renewcommand{\refname}{\normalsize Fullpaper}

\begin{thebibliography}{XXXX}

	\bibitem[MSF6]{MSF6}  
	\newblock Stefan M. Spann, Xingfeng Shao, Danny JJ. Wang, Christoph S. Aigner, \underline{Matthias Schloegl}, Kristian Bredies and Rudolf Stollberger.
	\newblock Robust single-shot acquisition of high resolution whole brain ASL images by combining time-dependent 2D CAPIRINHA sampling with spatio-temporal TGV reconstruction.
	\newblock NeuroImage, 2019, doi: 10.1016/j.neuroimage.2019.116337

	\bibitem[MSF5]{MSF5}  
	\newblock Oliver Maier, Jasper Schoormans, \underline{Matthias Schloegl}, Gustav J Strijkers, Andreas Lesch, Thomas Benkert, Tobias Block, Bram F Coolen, Kristian Bredies and Rudolf Stollberger. 
	\newblock Rapid T1 quantification from high resolution 3D data with model-based reconstruction.
	\newblock Magnetic Resonance in Medicine, 81(3): 2072-2089, 2018 , doi: 10.1002/mrm.27502

	\bibitem[MSF4]{MSF4}
	\newblock Andreas Lesch, \underline{Matthias Schloegl}, Martin Holler, Kristian Bredies and Rudolf Stollberger. 
	\newblock Ultrafast 3D Bloch-Siegert B1+ Mapping using Variational Modeling.
	\newblock Magnetic Resonance in Medicine, 81(2): 881-892, 2018, doi: 10.1002/mrm.27434

	\bibitem[MSF3]{MSF3}
 	\newblock Bernhard Neumayer, \underline{Matthias Schloegl}, Christian Payer, Thomas Widek, Sebastian Tschauner, Thomas Ehammer, Rudolf Stollberger and Martin Urschler.
 	\newblock Reducing acquisition time for MRI-based forensic age estimation. 
 	\newblock Scientific Reports, 8(1):2063, 2018, doi: 10.1038/s41598-018-20475

	\bibitem[MSF2]{MSF2}
 	\newblock \underline{Matthias Schloegl}, Martin Holler, Andreas Schwarzl, Kristian Bredies and Rudolf Stollberger. 
 	\newblock Infimal Convolution of Total Generalized Variation Functionals for dynamic MRI.
 	\newblock Magnetic Resonance in Medicine, 78(1): 142-144, 2017, doi: 10.1002/mrm.26352
 
 	\bibitem[MSF1]{MSF1}    
  	\newblock Diego Salas-Gonzalez, J.M. Gorriz, Javier Ramirez, \underline{Matthias Schloegl}, Elmar Wolfgang Lang, Andres Ortiz.
  	\newblock Parameterization of the distribution of white and grey matter in MRI using the $ \alpha$-stable distribution.
  	\newblock Comp. in Bio. and Med. 43(5): 559-567, 2013, doi: 10.1016/j.compbiomed.2013.01.003
  
\end{thebibliography}

\renewcommand{\refname}{\normalsize Conference proceedings}

\begin{thebibliography}{XXXX}

	\bibitem[MSC25]{MSC25}
	\newblock Optimal Transport Based Convex Hybrid Image and Motion-Field Reconstruction
	\newblock Ingmar Middelhoff, \underline{Matthias Schloegl}, Adrian Martin Fernandez, Silvio Fanzon, Kristian Bredies, Rudolf Stollberger.
	\newblock Proc. Intl. Soc. Mag. Reson. Med. 29 (2021), online



	\newblock 3D Bloch-Siegert EPI B1+-mapping.
	\newblock Andreas Johann Lesch, Christoph Stefan Aigner, Stefan Manfred Spann, \underline{Matthias Schloegl}, Rudolf Stollberger.
	\newblock Proc. Intl. Soc. Mag. Reson. Med. 27 (2019),  Montr\'eal, Canada


 	\bibitem[MSC24]{MSC24}
	\newblock 3D Bloch-Siegert EPI B1+-mapping.
	\newblock Andreas Johann Lesch, Christoph Stefan Aigner, Stefan Manfred Spann, \underline{Matthias Schloegl}, Rudolf Stollberger.
	\newblock Proc. Intl. Soc. Mag. Reson. Med. 27 (2019),  Montr\'eal, Canada

	\bibitem[MSC23]{MSC23}  
	\newblock Improving temporal resolution of 3D Arterial Spin Labeling perfusion imaging by combining CAIPIRINHA encoding and spatio-temporal TGV reconstruction.
    \newblock Stefan Spann, Xingfeng Shao, Danny Wang, Christoph Aigner, \underline{Matthias Schloegl}, Kristian Bredies, Rudolf Stollberger.
	\newblock Proc. Intl. Soc. Mag. Reson. Med. 27 (2019),  Montr\'eal, Canada

	\bibitem[MSC22]{MSC22}  
	\newblock Dynamic Multi-Coil Reconstruction using Variational Networks.
	\newblock Kerstin Hammernik, \underline{Matthias Schloegl}, Erich Kobler, Rudolf Stollberger, Thomas Pock.
	\newblock Proc. Intl. Soc. Mag. Reson. Med. 27 (2019),  Montr\'eal, Canada

	\bibitem[MSC21]{MSC21}  
	\newblock Oliver Maier, \underline{Matthias Schloegl}, Kristian Bredies, Rudolf Stollberger.
 	\newblock 3D Model-Based Parameter Quantification on Resource Constrained Hardware using Double-Buffering.
	\newblock Proc. Intl. Soc. Mag. Reson. Med. 27 (2019),  Montr\'eal, Canada

	\bibitem[MSC20]{MSC20}  
	\newblock Stefan Spann, Christoph Aigner, \underline{Matthias Schloegl}, Andreas Lesch, Kristian Bredies, Stefan Ropele, D. Pinter, Lukas Pirpamer and Rudolf Stollberger. 
	\newblock Acceleration of arterial spin labeling data using spatio-temporal total generalized variation (TGV) reconstruction. 
	\newblock Proc. Intl. Soc. Mag. Reson. Med. 26 (2018), Paris, France

	\bibitem[MSC19]{MSC19}  
	\newblock Stefan Spann, \underline{Matthias Schloegl}, Christoph Aigner, Karl Koschutnig, Martin Holler, Kristian Bredies and Rudolf Stollberger. 
	\newblock Denoising of functional Arterial Spin Labeling (fASL) perfusion data using infimal convolution of total generalized variation functionals (ICTGV). 
	\newblock Proc. Intl. Soc. Mag. Reson. Med. 26 (2018), Paris, France
	
	\bibitem[MSC18]{MSC18}  
	\newblock Oliver Maier, \underline{Matthias Schloegl}, Jasper Schoormans, Bram Coolen, Tobias Block, Thomas Benkert, Gustav Strijkers, and Rudolf Stollberger. 
	\newblock High Resolution T1 quantification from golden-angle radial 3D acquisitions. 
	\newblock Proc. Intl. Soc. Mag. Reson. Med. 26 (2018), Paris, France
	
	\bibitem[MSC17]{MSC17}  
	\newblock \underline{Matthias Schloegl}, Gernot Reishofer, Martin Holler, Thomas Benkert, Ulrike Wiesspeiner, Kristian Bredies, Kai-Tobias Block, Rudolf Stollberger. 
	\newblock Dynamic CE-MRA with high temporal resolution by combining radial acquisition and variational reconstruction.
	\newblock Proc. ESMRMB (2017): 344, Barcelona, Spain

	\bibitem[MSC16]{MSC16}  
  	\newblock \underline{Matthias Schloegl}, Martin Holler, Oliver Maier, Thomas Benkert, Kristian Bredies, Kai Tobias Block, Rudolf Stollberger.
  	\newblock Highly Accelerated Quantitative MRI with ICTGV Regularized Reconstruction.
  	\newblock Proc. Intl. Soc. Mag. Reson. Med. 25 (2017), Honululu, Hawaii, USA
 
 	\bibitem[MSC15]{MSC15} 
   	\newblock \underline{Matthias Schloegl}, Stefan Spann, Christoph Aigner, Martin Holler, Kristian Bredies, Rudolf Stollberger. 
   	\newblock Improved Denoising of Dynamic Arterial Spin Labeling with Infimal Convolution of Total Generalized Variation Functionals (ICTGV).
   	\newblock Proc. Intl. Soc. Mag. Reson. Med. 25 (2017), Honululu, Hawaii, USA
   
   	\bibitem[MSC14]{MSC14}
   	\newblock Oliver Maier, \underline{Matthias Schloegl}, Andreas Lesch, Andreas Petrovic, Martin Holler, Kristian Bredies, Thomas Pock, Rudolf Stollberger. 
   	\newblock Improved Accelerated Model-based Parameter Quantification with Total-Generalized-Variation Regularization.
   	\newblock Proc. Intl. Soc. Mag. Reson. Med. 25 (2017), Honululu, Hawaii, USA
   
   	\bibitem[MSC13]{MSC13}
    \newblock Andreas Lesch, \underline{Matthias Schloegl}, Rudolf Stollberger.
    \newblock Robust Accelerated Reconstruction for Bloch-Siegert B1-mapping.
    \newblock Proc. Intl. Soc. Mag. Reson. Med. 25 (2017), Honululu, Hawaii, USA
    
    \bibitem[MSC12]{MSC12}
    \newblock Bernhard Neumayer, \underline{Matthias Schloegl}, Christian Payer, Thomas Widek, Thomas Ehammer, Rudolf Stollberger, M. Urschler.
    \newblock Accuracy of Age Estimation based on Undersampled MR Images of the Hand.
    \newblock Proc. Intl. Soc. Mag. Reson. Med. 25 (2017), Hawaii, USA
     
    \bibitem[MSC11]{MSC11}
    \newblock Bernhard Neumayer, \underline{Matthias Schloegl}, Christian Payer, Thomas Widek, Thomas Ehammer, Rudolf Stollberger, M. Urschler.
    \newblock Acceleration of MR Measurements for Age Estimation.
    \newblock Proc. ESMRMB (2016): 344, Vienna, Austria
     
    \bibitem[MSC10]{MSC10}
    \newblock \underline{Matthias Schloegl}, Martin Holler, Andreas Schwarzl, Kristian Bredies, Rudolf Stollberger.
    \newblock ICTGV Reconstruction of DCE golden-angle radial VIBE data. 
    \newblock Proc. ESMRMB (2016): 290, Vienna, Austria 
     
    \bibitem[MSC9]{MSC9}
    \newblock Oliver Maier, \underline{Matthias Schloegl}, Andreas Lesch , Andreas Petrovic, Rudolf Stollberger.
    \newblock Accelerated T1-Mapping with iteratively TV regularized Gauss-Newton Method. 
    \newblock Proc. ESMRMB (2016): 205, Vienna, Austria 
     
    \bibitem[MSC8]{MSC8}
    \newblock \underline{Matthias Schloegl}, Bernhard Neumayer, Thommas Ehammer, Thomas Widek, Christian Payer, Martin Urschler, Rudolf Stollberger. 
    \newblock Validation of TGV regularized accelerated MR reconstruction by age estimation. 
    \newblock Proc. ESMRMB (2016): 111, Vienna, Austria 
     
	\bibitem[MSC6]{MSC6}
    \newblock Andreas Lesch, \underline{Matthias Schloegl}, Martin Holler and Rudolf Stollberger. 
    \newblock Highly Accelerated Bloch-Siegert B1+ Mapping Using Variational Modeling. 
    \newblock Proc. Intl. Soc. Mag. Reson. Med. 24 (2016), Singapur, Singapur
         
	\bibitem[MSC5]{MSC5}
	\newblock \underline{Matthias Schloegl}, Martin Holler, Kristian Bredies, Karl Kunisch, and Rudolf Stollberger.
	\newblock ICTGV Regularization for Highly Accelerated Dynamic MRI.
	\newblock Proc. Intl. Soc. Mag. Reson. Med. 23, Toronto, Canada (summa cum laude award)

	\bibitem[MSC4]{MSC4}
	\newblock \underline{Matthias Schloegl}, Martin Holler, Kristian Bredies, and Rudolf Stollberger. 
	\newblock A Variational Approach for Coil-Sensitivity Estimation for Undersampled Phase-Sensitive Dynamic MRI Reconstruction
	\newblock Proc. Intl. Soc. Mag. Reson. Med. 23, Toronto, Canada

	\bibitem[MSC3]{MSC3}
	\newblock \underline{Matthias Schloegl}, Clemens Diwoky, and Rudolf Stollberger.
	\newblock Motion detection for 3D radial balanced SSFP sequences.
	\newblock Proc. Intl. Soc. Mag. Reson. Med. 22, Milan, Italy

	\bibitem[MSC2]{MSC2}
	\newblock \underline{Matthias Schloegl}, Florian Knoll, Katharina Gruber, Franz Ebner, and Rudolf Stollberger. 
	\newblock Quantitative Evaluation of Non-Linear Reconstruction Methods in MRI. 
	\newblock Proc. Intl. Soc. Mag. Reson. Med. 21, Salt-Lake-City, Utah, USA

	\bibitem[MCS1]{MCS1}
	\newblock Diego Salas-Gonzalez, J.M. G\'orriz, Javier Ram\'irez, \underline{Matthias Schloegl}, Elmar Wolfgang Lang.
	\newblock Bayesian Segmentation of Magnetic Resonance Images Using the $\alpha$-stable distribution.
	\newblock HAIS 2011, Wroclaw, Poland, May 23-25, 2011
	 

\end{thebibliography}
